Attachment Analysis: Report Project

### 2021-06-29 Documents/Report-Project/Report-analysis.Rmd
init repo

# Descriptive Statistics

## Dependent Variable

### Externalizing
```{r}
ggplot(data_munged) +
  geom_bar(aes(x = externalizing_sum, fill = genere), alpha = 0.7) +
  facet_grid(genere ~ .)
```

### Internalizing
```{r}
ggplot(data_munged) +
  geom_bar(aes(x = internalizing_sum, fill = genere), alpha = 0.7) +
  facet_grid(genere ~ .)
```

# Cluster Analysis

## Mother

```{r}
plot(cluster_mother_tat, main = "Dendrogramma")
rect.hclust(cluster_mother_tat, k=4, border="red")
```

Frequencies

```{r, echo = TRUE}
table(data_cluster_tat$cluster_mother_tat)

prop.table(table(data_cluster_tat$cluster_mother_tat))

prop.table(table(data_cluster_tat$cluster_mother_tat,
                 data_cluster_tat$genere),2)

summary(table(data_cluster_tat$cluster_mother_tat,
              data_cluster_tat$genere))
```

Plot Scores

```{r}
plot_scores_mother(data = data_cluster_tat)
```

#### Mclust check

```{r}
plot(mclust_mother)
summary(mclust_mother)
```

## Father

```{r}
plot(cluster_father_tat, main = "Dendrogramma")
rect.hclust(cluster_father_tat, k=4, border="red")
```

Frequencies

```{r, echo = TRUE}
table(data_cluster_tat$cluster_father_tat)

prop.table(table(data_cluster_tat$cluster_father_tat))

prop.table(table(data_cluster_tat$cluster_father_tat,
                 data_cluster_tat$genere),2)

summary(table(data_cluster_tat$cluster_father_tat,
              data_cluster_tat$genere))
```

Plot Scores

```{r}
plot_scores_father(data = data_cluster_tat)
```

#### Mclust check

```{r}
plot(mclust_father)
summary(mclust_father)
```

# Statistical Approach

In this section we describe the statistical approach. First we define the statistical model used to describe the data generative process. Subsequently, the approach for testing hypotheses with inequality and equality constraints is discussed. Finally, the Gibbs sampler to estimate the model with inequality constraints is presented.

## Model Definition

### Psychologial Background

@@

### Zero Inflated Poisson (ZIP) {#model}

@@

## Test of Hypotheses with Inequality and Equality Constraints

@@

### Inequality Constraints: A First Approach

@@

### Inequality and Equality Constraints: A Second Approach {#in-eq-const}

@@

#### @mulderBayesFactorTesting2019 {#mulder}

@@

#### @guApproximatedAdjustedFractional2018

@@

### Present Study

@@

@@

## Estimating the Constrained Model

@@

### STAN Approach

@@

#### Issues

@@

### Gibbs Sampler Approach

@rodriguez-yamEfficientGibbsSampling implemented a Gibbs sampler for a ZIP model, whereas @ katoBayesianApproachInequality2006 presented a Gibbs sampler to estimate a model with inequality constraints using truncated normal distributions. We would like to put together the two methods in order to estimate a ZIP model with inequality constraints on the parameters.

@@

#### Conditional Posterior Distributions

@@

#### Conditional Posteriors

@@

Nel lavoro di @rodriguez-yamEfficientGibbsSampling, inoltre, fanno una cosa strana nel senso che definiscono $\lambda = X\beta+\epsilon$ e oltre a mettere le prior sui parametri $\beta$ la mettono anche su $\lambda$. Non capisco:

@@

#### Including Inequality Constraints

@@

### Issue

@@

## brms

```{r}
summary(fit_int)
```

```{r}
brms::conditional_effects(fit_int, ask= FALSE)
```

### Prior

```{r, echo = TRUE}
brms::get_prior(brms::bf(
      internalizing_sum ~ genere + cluster_mother_tat + cluster_father_tat,
      zi ~ genere + cluster_mother_tat + cluster_father_tat),
      data = data_cluster_tat,
      family = brms::zero_inflated_poisson())
```

# References {-}

>>>>

In this Reeport we describe the statistical approach. First we define the statistical model used to describe the data generative process. Subsequently, the approach for testing hypotheses with inequality and equality constraints is discussed. Finally, the Gibbs sampler to estimate the model with inequality constraints is presented.

# Model Definition

## Psychologial Background

@@

## Zero Inflated Poisson (ZIP) {#model}

@@

# Test of Hypotheses with Inequality and Equality Constraints

@@

## Inequality Constraints: A First Approach

@@

## Inequality and Equality Constraints: A Second Approach {#in-eq-const}

@@

### @mulderBayesFactorTesting2019 {#mulder}

@@

### @guApproximatedAdjustedFractional2018

@@

## Present Study

@@

## Issues

@@

# Estimating the Constrained Model

@@

## STAN Approach

@@

@@

## Gibbs Sampler Approach

@rodrigues-mottaZeroInflatedPoissonModel2007 implemented a Gibbs sampler for a ZIP model, whereas @ katoBayesianApproachInequality2006 presented a Gibbs sampler to estimate a model with inequality constraints using truncated normal distributions. We would like to put together the two methods in order to estimate a ZIP model with inequality constraints on the parameters.

@@

### Conditional Posterior Distributions

@@

#### Conditional Posteriors {-}

@@

Nel lavoro di @rodrigues-mottaZeroInflatedPoissonModel2007, inoltre, fanno una cosa strana nel senso che definiscono $\lambda = X\beta+\epsilon$ e oltre a mettere le prior sui parametri $\beta$ la mettono anche su $\lambda$. Non capisco:

@@

### Including Inequality Constraints

@@

## Issue

@@

# References
